Stabilization-Free Virtual Element Methods

### 2022-06-19 stabfreevem_sinum.tex
proofreading

The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the inner product $(\cdot, \cdot)_K$. The norm equivalence \eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be sufficiently large compared with the virtual element space $V_k(K)$.
In standard virtual element methods, $Q_{k-1}^{K}\nabla v$ \cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$ \cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016} are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the $(k-1)$th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and $\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$th order polynomial space $\mathbb P_{k}(K)$.
While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$th order or $(k-1)$th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$th order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition $\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element space for $k=0$, with some constraints. To ensure the $L^2$ projection $Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable for virtual element function $v\in V_k(K)$, we require $\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and $\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$ is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  
Based on these considerations and the direct decomposition of an $H(\div)$-conforming macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the $L^2$ norm equivalence.
By the way, we use the matrix-vector language to review a conforming finite element for differential $(d-2)$-form in \cite{ArnoldFalkWinther2006,Arnold2018}.

% $$
% \|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
% $$

@@

For $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit outward normal vector to $\partial F$.

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big).
\end{equation}
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
\[
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
\]
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
\[
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
\]
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

\begin{lemma}\label{lem:PkKbubblecharac}
For $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$, $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$, if and only if 
\begin{equation}\label{eq:PkKbubblecharac}
\boldsymbol{\tau}=\sum_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
\end{equation}
for some $q_{ij}\in\mathbb P_{k-2}(T)$. Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ is the basis of antisymmetric matrice space $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
\[
\boldsymbol{N}_{ij}:\skw({\boldsymbol n_l\boldsymbol n_m^{\intercal}})=\delta_{il}\delta_{jm},\quad 1\leq i<j\leq d,\; 1\leq l<m\leq d.
\]
\end{lemma}
\begin{proof}
For $1\leq l\leq d$ but $l\neq i, j$, by the definition of $\boldsymbol{N}_{ij}$, it holds $\boldsymbol{N}_{ij}\boldsymbol{n}_l=\boldsymbol{0}$. Hence for $
\boldsymbol{\tau}=\sum\limits_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
$, obviously we have $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$.

@@

Let 
\[
\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
\]
Due to DoFs \eqref{Vpdivdof1}-\eqref{Vpdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
\end{align}

@@

% \begin{lemma}
% It holds the coercivity
% \begin{equation}\label{eq:cfmahcoercivity}
% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
% \end{equation}  
% \end{lemma}
% \begin{proof}
% Due to \eqref{eq:cfmgradVknormequivalence}, we have
% $$
% \sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
% $$
% which implies the coercivity \eqref{eq:cfmahcoercivity}.
% \end{proof}

@@

\subsection{Error analysis}
\begin{theorem}
Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}. Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
\begin{equation}\label{eq:cfmerrorestimateH1}
|u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
\end{equation}
\end{theorem}
\begin{proof}
Take any $v_h\in V_h$. 
Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
\[
\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
\]
\[
a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
\]
Combining the last two inequalities gives
\[
a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
\]
By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
\begin{align*}
|v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
\end{align*}
Hence we get from the triangle inequality and the last two inequalities that
\begin{align*}  
|u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
&\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
\end{align*}
By the arbitrariness of $v_h\in V_h$, we derive
\[
|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
\]
At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
\end{proof}

@@

\section{Numerical examples}\label{sec:numericalexamps}
In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
virtual element method \eqref{eq:cfmvem}.

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ mesh are shown in Figure \ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the conforming virtual element method \eqref{eq:vem} are presented in Figure \ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:errorestimateH1}.
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}

>>>>

The key to construct stabilization-free virtual element methods is to find a finite-dimensional space $\mathbb{V}(K)$ and a projector $Q_K$ onto space $\mathbb{V}(K)$ such that
\begin{enumerate}[(C1)]
\item It holds the norm equivalence 
\begin{equation}\label{intro:gradVknormequiv} 
\|Q_{K}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K)
\end{equation}
on shape function space $V_k(K)$ of virtual elements;
\item The projection $Q_{K}\nabla v$ is computable based on the degrees of freedom (DoFs) of virtual elements for $v\in V_k(K)$.
\end{enumerate}
We can choose $Q_{K}$ as the $L^2$-orthogonal projector with respect to the
inner product $(\cdot, \cdot)_K$. The norm equivalence
\eqref{intro:gradVknormequiv} implies space $\mathbb{V}(K)$ should be
sufficiently large compared with the virtual element space $V_k(K)$.  In
standard virtual element methods, $Q_{k-1}^{K}\nabla v$
\cite{BeiraodaVeigaBrezziMariniRusso2016} or $\nabla\Pi_k^{K}v$
\cite{BeiraoBrezziCangianiManziniEtAl2013,BeiraoBrezziMariniRusso2014,AhmadAlsaediBrezziMariniEtAl2013,AyusodeDiosLipnikovManzini2016}
are used, where $Q_{k-1}^{K}$ is the $L^2$-orthogonal projector onto the
$(k-1)$-th order polynomial space $\mathbb P_{k-1}(K; \mathbb{R}^d)$, and
$\Pi_k^{K}$ is the $H^1$ projection operator onto the $k$-th order polynomial
space $\mathbb P_{k}(K)$.  While only
\[
\|Q_{k-1}^{K}\nabla v\|_{0,K}\lesssim \|\nabla v\|_{0,K}, \quad \|\nabla\Pi_k^{K}v\|_{0,K}\lesssim \|\nabla v\|_{0,K}
\]
hold
rather than the norm equivalence \eqref{intro:gradVknormequiv}, then the additional stabilization term is usually necessary to ensure the coercivity of the discrete bilinear form.
To remove the additional stabilization term, $\mathbb{V}(K)$ is taken as $\mathbb P_{l}(K; \mathbb{R}^d)$ with large enough $l$ even for the lowest order case $k=1$ in \cite{BerroneBorioMarcon2021,BerroneBorioMarcon2022,DAltriMirandaPatrunoSacco2021}, and the virtual element space $V_k(K)$ has to be modified accordingly to make $Q_{l}^{K}\nabla v$ computable.
Instead, we employ $k$-th order or $(k-1)$-th order $H(\div)$-conforming macro finite elements as $\mathbb{V}(K)$ in this paper, and keep the virtual element space $V_k(K)$ as usual ones.

We first construct $H(\div)$-conforming macro finite elements based on a
simplicial partition $\mathcal T_K$ of polytope $K$ in arbitrary dimension. The
shape function space $\mathbb{V}_{k}^{\rm div}(K)$ is a subspace of the $k$-th
order Brezzi-Douglas-Marini (BDM) element space on the simplicial partition
$\mathcal T_K$ for $k\geq1$ and the lowest order Raviart-Thomas (RT) element
space for $k=0$, with some constraints. To ensure the $L^2$ projection
$Q_{K,k}^{\div}\nabla v$ onto space $\mathbb{V}_{k}^{\rm div}(K)$ is computable
for virtual element function $v\in V_k(K)$, we require
$\div\boldsymbol{\phi}\in\mathbb P_{\max\{k-1,0\}}(K)$ and
$\boldsymbol{\phi}\cdot\boldsymbol{n}$ on each $(d-1)$-dimensional face of $K$
is a polynomial for $\boldsymbol{\phi}\in\mathbb{V}_{k}^{\rm div}(K)$.  Based on
these considerations and the direct decomposition of an $H(\div)$-conforming
macro finite element space related to $\mathbb{V}_{k}^{\rm div}(K)$, we propose
the unisolvent DoFs for space $\mathbb{V}_{k}^{\rm div}(K)$, and establish the
$L^2$ norm equivalence.  By the way, we use the matrix-vector language to review
a conforming finite element for differential $(d-2)$-form in
\cite{ArnoldFalkWinther2006,Arnold2018}.

% \[
% \|Q_{K,k-1}^{\div}\nabla v\|_{0,K}\eqsim \|\nabla v\|_{0,K} \quad \forall~v\in V_k(K).
% \]

@@

For $d$-dimensional simplex $T$,
let $F_i\in\mathcal F(T)$ be the $(d-1)$-dimensional face opposite to vertex $\texttt{v}_i$, $\boldsymbol n_i$ be the unit outward normal to the face $F_i$, and $\lambda_i$ be the barycentric coordinate of $\boldsymbol x$ corresponding to vertex $\texttt{v}_i$, for $i=0, 1, \cdots, d$.
Clearly $\{ \boldsymbol n_1, \boldsymbol n_2, \cdots, \boldsymbol n_d \}$ spans $\mathbb R^d$, and $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$ spans the antisymmetric space $\mathbb K$. 
For $F\in\mathcal F(T)$, let $\mathcal{E}(F):=\{e\in\mathcal{E}(T): e\subset\partial F\}$.
For $e\in \mathcal E(F)$, denote by $\boldsymbol{n}_{F,e}$ be the unit vector outward normal to $\partial F$ but parallel to $F$.

@@

\begin{lemma}
It holds the decomposition
\begin{equation}\label{eq:Pkskwtensordecomp}  
\mathbb P_{k-2}(T;\mathbb K)=\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\oplus\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big),
\end{equation}
where $\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})$ means the kernel of operator $\boldsymbol{x}: \mathbb P_{k-2}(T;\mathbb K)\to\mathbb P_{k-1}(T;\mathbb R^d)$.
\end{lemma}
\begin{proof}
Thanks to decomposition \eqref{eq:Pkvectordecomp}, we have 
\[
\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\skw\nabla(\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}).
\]
By Lemma~\ref{lem:skwgrad}, $\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)\cap\big(\mathbb P_{k-2}(T;\mathbb K)\cap\ker(\boldsymbol{x})\big)=\{\boldsymbol{0}\}$. Then we only need to check dimensions.
Due to complex \eqref{eq:polycomplex1},
\begin{equation}\label{eq:20220324-1}  
\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-1}(T;\mathbb R^d)-\dim\nabla\mathbb P_k(T).
\end{equation}
On the other side, by space decomposition \eqref{eq:Pkvectordecomp},
\[
\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}=\dim\mathbb P_{k-1}(T;\mathbb R^{d})-\dim\nabla\mathbb P_k(T).
\]
Hence $\dim\skw\nabla\mathbb P_{k-1}(T;\mathbb R^d)=\dim\mathbb P_{k-2}(T;\mathbb K)\boldsymbol{x}$, which yields \eqref{eq:Pkskwtensordecomp}.
\end{proof}

@@

\begin{lemma}\label{lem:PkKbubblecharac}
For $\boldsymbol{\tau}\in\mathbb P_k(T;\mathbb K)$, $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$, if and only if 
\begin{equation}\label{eq:PkKbubblecharac}
\boldsymbol{\tau}=\sum_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
\end{equation}
for some $q_{ij}\in\mathbb P_{k-2}(T)$. Here $\{\boldsymbol{N}_{ij}\}_{1\leq i<j\leq d}$ denotes the basis of $\mathbb K$ being dual to $\{\skw({\boldsymbol n_i\boldsymbol n_j^{\intercal}})\}_{1\leq i<j\leq d}$, i.e.,
\[
\boldsymbol{N}_{ij}:\skw({\boldsymbol n_l\boldsymbol n_m^{\intercal}})=\delta_{il}\delta_{jm},\quad 1\leq i<j\leq d,\; 1\leq l<m\leq d.
\]
\end{lemma}
\begin{proof}
For $1\leq l\leq d$ but $l\neq i, j$, by the definition of $\boldsymbol{N}_{ij}$, it holds $\boldsymbol{N}_{ij}\boldsymbol{n}_l=\boldsymbol{0}$. Hence for $
\boldsymbol{\tau}=\sum\limits_{1\leq i<j\leq d}\lambda_i\lambda_jq_{ij}\boldsymbol{N}_{ij}
$, obviously we have $\boldsymbol{\tau}\boldsymbol{n}|_{F_i}=\boldsymbol{0}$ for $i=1,\ldots, d$.

@@

Let 
\[
\mathbb{V}_{k-1}^{\rm div}(K):=\{\boldsymbol{\phi}\in\boldsymbol{V}_{k-1}^{\rm div}(K): \boldsymbol{\phi}\cdot\boldsymbol{n}|_F\in\mathbb P_{k-1}(F) \quad\forall~F\in\mathcal F(K)\}.
\]
Due to DoFs \eqref{Vdivdof1}-\eqref{Vdivdof3} for $\boldsymbol{V}_{k-1}^{\rm div}(K)$, a set of unisolvent DoFs for $\mathbb{V}_{k-1}^{\rm div}(K)$ is 
\begin{align}
    (\boldsymbol{\phi}\cdot\boldsymbol{n}, q)_F & \quad\forall~q\in\mathbb P_{k-1}(F) \textrm{ on each }  F\in\mathcal F(K), \label{Vpdivdof1}\\
    (\div\boldsymbol{\phi}, q)_K & \quad\forall~q\in\mathbb P_{\max\{k-2,0\}}(K)/\mathbb R, \label{Vpdivdof2} \\
    (\boldsymbol{\phi}, \boldsymbol{q})_K & \quad\forall~\boldsymbol{q}\in \div\mathring{\boldsymbol{V}}_{k}^{d-2}(K). \label{Vpdivdof3}
\end{align}

@@

% \begin{lemma}
% It holds the coercivity
% \begin{equation}\label{eq:cfmahcoercivity}
% |v_h|_1^2\lesssim a_h(v_h, v_h)\quad\forall~v_h\in V_h.
% \end{equation}  
% \end{lemma}
% \begin{proof}
% Due to \eqref{eq:cfmgradVknormequivalence}, we have
% \[
% \sum_{K\in\mathcal T_h}\|\nabla v_h\|_{0,K}^2\lesssim \sum_{K\in\mathcal T_h}\|Q_{K,k}^{\div}\nabla v_h\|_{0,K}^2\leq a_h(v_h, v_h)\quad\forall~v_h\in V_h,
% \]
% which implies the coercivity \eqref{eq:cfmahcoercivity}.
% \end{proof}

@@

\subsection{Error analysis}
\begin{theorem}\label{thm:cfmerrorestimateH1}
Let $u\in H_0^1(\Omega)$ be the solution of problem \eqref{eq:ellipitc2ndproblem}, and $u_h\in V_h$ be the solution of the virtual element method \eqref{eq:cfmvem}. Assume $u\in H^{k+1}(\Omega)$ and $f\in H^{k-1}(\Omega)$. Then
\begin{equation}\label{eq:cfmerrorestimateH1}
|u-u_h|_1\lesssim h^k(|u|_{k+1}+|f|_{k-1}).
\end{equation}
\end{theorem}
\begin{proof}
Take any $v_h\in V_h$. 
Applying the same argument as in Theorem \ref{thm:errorestimateH1}, we have
\[
\|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0+\|u-Q_hv_h\|_0\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1,
\]
\[
a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim \|\nabla u-Q_{h,k}^{\div}\nabla v_h\|_0|v_h-u_h|_1+\|u-Q_hv_h\|_0\|v_h-u_h\|_0.
\]
Combining the last two inequalities gives
\[
a_h(v_h, v_h-u_h)-a(u,v_h-u_h)\lesssim(\|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1)|v_h-u_h|_1.
\]
By the coercivity \eqref{eq:cfmahcoercivity}, \eqref{eq:cfmvem}, \eqref{eq:ellipitc2ndproblemweakform} and the error estimate of $Q_h^0$,
\begin{align*}
|v_h-u_h|_1^2&\lesssim a_h(v_h-u_h, v_h-u_h)=a_h(v_h, v_h-u_h)-(f, Q_h(v_h-u_h)) \\
&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h) \\
% &\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+(f-Q_hf, v_h-u_h-Q_h^0(v_h-u_h)) \\
&\lesssim a_h(v_h, v_h-u_h)-a(u,v_h-u_h)+h\|f-Q_hf\|_0|v_h-u_h|_1.
\end{align*}
Hence we get from the triangle inequality and the last two inequalities that
\begin{align*}  
|u-u_h|_1&\leq|u-v_h|_1+|v_h-u_h|_1 \\
&\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+|u-v_h|_1+h\|f-Q_hf\|_0.
\end{align*}
By the arbitrariness of $v_h\in V_h$, we derive
\[
|u-u_h|_1\lesssim \|\nabla u-Q_h^{k-1}\nabla u\|_0+\|u-Q_hu\|_0+h\|f-Q_hf\|_0+\inf_{v_h\in V_h}|u-v_h|_1.
\]
At last, \eqref{eq:cfmerrorestimateH1} follows from the last inequality, the error estimates of $Q_h^{k-1}$ and $Q_h$, and the approximation of $V_h$ \cite{Huang2021,ChenHuang2018,BrennerSung2018,BeiraodaVeigaLovadinaRusso2017}.
\end{proof}

@@

\section{Numerical results}\label{sec:numericalexamps}
In this section, we will numerically verify the convergence of the nonconforming virtual element method \eqref{eq:vem} and the conforming
virtual element method \eqref{eq:cfmvem}.
The numerical example is implemented by using the FEALPy package \cite{fealpy}

@@

The rectangular domain $\Omega$ is partitioned by the convex polygon mesh
$\mathcal T_0$ and non-convex polygon mesh $\mathcal T_1$, respectively, 
In both virtual element methods \eqref{eq:vem} and \eqref{eq:cfmvem}, we choose $k = 1, 2, 5$.
The numerical results of the nonconforming virtual element method \eqref{eq:vem} on meshes $\mathcal T_0$ and $\mathcal T_1$ mesh are shown in Figure \ref{fig:rate1}. We can see that $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0=O(h^{k})$, which coincide with Theorem~\ref{thm:errorestimateH1}.
And the numerical results of the conforming virtual element method \eqref{eq:cfmvem} are presented in Figure \ref{fig:rate2}. Again $\|u - Q_h u_h\|_0=O(h^{k+1})$ and $\|\nabla u - Q_{h, k}^{\div}\nabla u_h\|_0=O(h^{k})$, which confirm the
theoretical convergence rate in Theorem~\ref{thm:cfmerrorestimateH1}.
\begin{figure}[htbp]
\centering
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_convex.pdf}
%\caption{Numberical result of example with $\mathcal T_0$.}
\end{minipage}%
\begin{minipage}[t]{0.49\linewidth}
\centering
\includegraphics[width=6cm]{./figures/ncvem_nonconvex.pdf}
%\caption{[Numberical result of example with $\mathcal T_1$].}
\end{minipage}%
\centering
\caption{Errors $\|u - Q_h u_h\|_0$ and $\|\nabla u - Q_{h, k-1}^{\div}\nabla_h u_h\|_0$ 
of nonconforming virtual element method \eqref{eq:vem} on 
$\mathcal T_0$(left) and $\mathcal T_1$(right) with $k=1, 2, 5$.}
\label{fig:rate1}
\end{figure}
